A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-09-10 paper/paper.tex
paper: MAJ semi-{simplicial, cubical} sets

% Simplicial and Cubical sets
\newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
\renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}

@@

@@

\subsection{Semi-cubical sets}
\begin{definition}[\Cube{}]
  \begin{align*}
    \obj(\Cube{}) & := \Nat                                                                                                             \\
    \hom(p, n)    & := \{(i_{p + 1}, \epsilon_{p + 1}) \ldots, (i_n, \epsilon_n) \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\}
  \end{align*}
\end{definition}

\begin{example}[$\Cube{0}$, $\Cube{1}$ and $\Cube{2}$]
  $\Cube{0}$ can be drawn as:

@@

  $\Cube{1}$ can be drawn as:

@@

  and $\Cube{2}$ can be drawn as a filled square:

@@

Here, $\I{n}$ serves the purpose of \sq{n}, but this change will cascade into other definitions. In view of defining a category \CSet, we will restrict the morphisms in \Cube{}.

\begin{definition}[\Cube{}]
  \begin{align*}
    \obj(\Cube{}) & := \I{n}                                           \\
    \mor(\Cube{}) & := \delta^\epsilon_i : \I{n + 1} \rightarrow \I{n}
  \end{align*}

  where $\delta^\epsilon_i$ must satisfy the corresponding face map condition:

  \begin{equation*}
    \delta^\epsilon_i \delta^\omega_j = \delta^\omega_{j - 1} \delta^\epsilon_i
  \end{equation*}

  where $\epsilon$ and $\omega$ correspond to opposite faces.
\end{definition}

\begin{definition}[\CSet]
  Just as in \SSet, we define semi-cubical sets as the functor category:

  \begin{equation*}
    \CSet := \Set^{\Cube{}^{op}}
  \end{equation*}
\end{definition}

@@

\begin{definition}[$\CSet$ in terms of objects and morphisms]
  \begin{align*}
    \obj(\CSet) & := X_n                                                   \\
    \mor(\CSet) & := X_\lambda, \text{where $\lambda$ is \Cube{}-morphism}
  \end{align*}

  where we term $X_n$ as the $n$-cubex, and $X_\lambda$ as the ``face map'', defined similarly:

  \begin{align*}
    X_n       & := X(\I{n}), \text{where X is the semi-cubical set} \\
    X_\lambda & := X(\lambda)
  \end{align*}
\end{definition}

>>>>

% Simplicial and Cubical sets
\newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
\newcommand{\Cube}{\ensuremath{\boldsymbol{\square}}}
\renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}

@@

\begin{definition}[$\Set_{\DeltaPlus}$]
  We define the category of augmented semi-simplicial sets as the functor category:

  \begin{equation*}
    \Set_{\DeltaPlus} := \Set^{\op{\DeltaPlus}}
  \end{equation*}
\end{definition}

@@

\subsection{Semi-cubical sets}
\begin{definition}[\Cube]
  \begin{align*}
    \obj(\Cube) & := \Nat                                                                                                             \\
    \hom(p, n)  & := \{(i_{p + 1}, \epsilon_{p + 1}) \ldots, (i_n, \epsilon_n) \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\} \\
    f \circ g   & := \text{concatenation of the sequences $f$ and $g$}
  \end{align*}
\end{definition}

\begin{definition}[\CSet]
  We define the category of semi-cubical sets as the functor category:

  \begin{equation*}
    \CSet := \Set^{\op{\Cube}}
  \end{equation*}
\end{definition}

\begin{example}[$\Cube^0$, $\Cube^1$ and $\Cube^2$]
  $\Cube^0$ can be drawn as:

@@

  $\Cube^1$ can be drawn as:

@@

  and $\Cube^2$ can be drawn as a filled square:

@@

Here, $\I{n}$ serves the purpose of \sq{n}, but this change will cascade into other definitions. In view of defining a category \CSet, we will restrict the morphisms in \Cube.

@@
